Thermodynamic fragments in magic state theories

### 2020-07-15 magic_paper.tex
Added subsection Lorenz curves calculations temporarily, where I include all important results on our ncopy strange state lorenz curve calculations in the unital fragment

Lorenz curve analysis simplifies significantly in the unital fragment \nick{or so I thought initially}, because the invariant Wigner distribution is the uniform distribution depicted in~\cref{fig:maxmix}.
Therefore, $\W[\bmu]{(\frac{1}{d}\id)^{\otimes n}} = \frac{1}{d^{2n}}$ for all $\bmu \in \pd[d^n]$ and the Lorenz curve ordering only depends on $\rho$ \nick{rephrase}
The Lorenz curve $\lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}$ consists of $n+1$ line segments, with $n$ endpoints, or ``elbows'', between $(0,0)$ and $(1,1)$. 
The $k_\star$-th endpoint is the maximum in~\cref{eq:Skmax} occuring at 
\begin{equation}
	x_{k_\star} = \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right).
\end{equation}

All $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}, are given by the following sums, $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) =$
\begin{equation}\label{eq:leftelb}
	\left( \frac{1}{9^n} \sum\limits_{j=0}^{k-1} 8^{2j} \binom{n}{2j}, \frac{1}{3^n} \sum\limits_{j=0}^{k-1} 4^{2j} \binom{n}{2j} \right)
\end{equation}
for all elbows left of the maximum, $k = 1, \dots, k_\star = \floor{\frac{n}{2}}+1$ and $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) = (x_{k_\star}, L(k_\star)) + $
\begin{equation}\label{eq:rightelb}
	\left( \left(\frac{8}{9}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 8^{-(2j+1)} \binom{n}{2j+1}, \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 4^{-(2j+1)} \binom{n}{2j+1} \right),
\end{equation}
for all elbows right of the maximum, $k' = k_\star + 1, \dots, n$.

@@

>>>>

@@

\subsection{Lorenz curves calculations}

Lorenz curve analysis simplifies significantly in the unital fragment \nick{or so I thought initially}, because the invariant Wigner distribution is the uniform distribution depicted in~\cref{fig:maxmix}.
Therefore, $\W[\bmu]{(\frac{1}{d}\id)^{\otimes n}} = \frac{1}{d^{2n}}$ for all $\bmu \in \pd[d^n]$ and the ordering of the points on the Lorenz curve only depends on the ordering of the Wigner components of $\rho$.
The Lorenz curve $\lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}$ consists of $n+1$ line segments, with $n$ endpoints, or ``elbows'', between $(0,0)$ and $(1,1)$. 
The $k_\star$-th endpoint is the maximum in~\cref{eq:Skmax} occuring at 
\begin{equation}
	x_{k_\star} = \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right).
\end{equation}

We now investigate the location of all $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}.

Let $\bar n = 2\floor{\frac{n}{2}}$ be equal to $n$ if $n$ is even and $n-1$ if $n$ is odd.
Then, the positive components of the $n$-copy Strange state Wigner distribution $\W{\ketbra{\rm{S}}}$ are, in decreasing order, $6^{-n} 2^{\bar n} 2^{-j},\ j=0, 2, \dots, \bar n$ with respective multiplicites $8^{n-\bar n} 8^j \binom{n}{\bar n - j}$.
The negative components are, in decreasing order $-6^{-n} 2^j,\ j=1,3, \dots, n$ with respective multiplicities $8^n 8^{-j} \binom{n}{j}$.

Denote by $\Phi(m; n, p)$ the cumulative binomial distribution,
\begin{equation}
	\Phi(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}.
\end{equation}
Let $\Phi_+(m; n, p)$ denote the same sum but only considering the even indices, $j = 0, 2, \dots, m$ and similarly let $\Phi_-(m; n, p)$ denote the same sum but only considering the odd indices, $j = 1, 3, \dots, m$.

Assume $n$ is even, so that $\bar n = n$.
Then we can express any elbow on the $n$-copy Strange state Lorenz curve as
\begin{align}
	L_+(m; n) &= \left(\frac{5}{3}\right)^n \Phi_+\left(m;n,\frac{4}{5}\right) \label{eq:leftelb}\\
	L_-(m; n) &= L_\star - \left(\frac{5}{3}\right)^n \Phi_-\left(m;n,\frac{1}{5}\right), \label{eq:rightelb}
\end{align}
where $L_\star = L_+(n; n)$ is the maximum of the curve and $L_+, L_-$ indicate points on the left, right of the curve respectively for some index $m$.

The locations of the elbows are at
\begin{align}
	x_+(m; n) &= \Phi_+\left(m;n,\frac{8}{9}\right) \\
	x_-(m; n) &= x_\star + \Phi_-\left(m;n,\frac{1}{9}\right),
\end{align}
where $x_\star = x_+(n; n)$ is the location of the maximum.
